\section{Psalm 50 Comments}

\subsection{Numeric Nuggets}
\textbf{13:} Verses 6, 13, and 20 contains 13 words. Verses 6, 11, and 20 contain 13 unique words. The 13-letter word ``righteousness'' is used in the chapter.

\newpage

\begin{mdframed}[style=MyFrame]
\begin{center}
\begin{longtable}{|p{.5in}|p{3.5in}|}

\caption[Corruption Alert: Psalm 50:23]{Corruption Alert: Psalm 50:23} \label{table:CorruptionProv18:1} \\ 

\hline  
\multicolumn{1}{|c|}{\textbf{Version}} & 
\multicolumn{1}{c|}{\textbf{Corruption}}  \\ \hline 
\endfirsthead
 
\multicolumn{2}{c}
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\  \hline  
\multicolumn{1}{|c|}{\textbf{Version}} & 
\multicolumn{1}{c|}{\textbf{Corruption}}  \\ \hline 
\endhead
 
\hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
\endfoot 
\textcolor[rgb]{0.00,0.00,1.00}{AV} & \textcolor[rgb]{0.00,0.00,1.00}{Whoso offereth praise glorifieth me: and to him that ordereth his conversation aright will I shew the salvation of God.} \\ \hline
%
ASV &  Whoso offereth the sacrifice of thanksgiving glorifieth me; And to him that ordereth his way aright Will I show the salvation of God. \\ \hline
%
CEB &  The one who offers a sacrifice of thanksgiving is the one who honors me.  And it is to the one who charts the correct path that I will show divine salvation.\\ \hline
%
ESV & The one who offers a sacrifice of thanksgiving is the one who honors me.     And it is to the one who charts the correct path that I will show divine salvation.”Read full chapter \\ \hline
%
NASV &  He who offers a sacrifice of thanksgiving honors Me; And to him who [a]orders his way aright I shall show the salvation of God.” \\ \hline
%
MEV & Whoever sacrifices a thank offering  glorifies Me and makes a way;  I will show him the salvation of God.\\ \hline
%
NIV &  Those who sacrifice thank offerings honor me,  and to the blameless[a] I will show my salvation.\\ \hline
%
NKJV &  Whoever offers praise glorifies Me; And to him who orders his conduct aright I will show the salvation of God.”\\ \hline
%
RSV &  He who brings thanksgiving as his sacrifice honors me;   to him who orders his way aright  I will show the salvation of God!\\ \hline

\multicolumn{2}{p{4.3in}}{{Modern translations, such as the ASV and others, strike out the first part of the verse, concealing the intent of mankind clearly revealed in scripture. }} \\ %\hline

\hline

\end{longtable}
\end{center}

\normalsize 
\end{mdframed}