\section{Psalm 26 Comments}

\subsection{Numeric Nuggets}
\textbf{13:} There are thirteen words in verses 2 and 13. There are 13 unique words in verses 3, 6, 10, and 12. The word ``I'' is used 13 times. The 13-letter word ``congregations'' is used in the chapter. 

\subsection{Introduction}
Compare with Psalm 1. Here David walks in integrity (Psalm 26:1), stands in an even place (Psalm 26:12), and does not sit with vain persons or evil doer (Psalm 26:4, 5).

\subsection{Psalm 26:1}
The word ``slide'' points to the word ``backslide'', which is NOT found in scripture. The words ``backslider'', ``backsliding'', and ``backslidings'' are. Forms of the word are found 13 times in Jeremiah.

\subsection{Psalm 26:12}
The word ``congreations'' is found 3 times in scripture, here and in Psalm 6:26 and 74:4.\footnote{\textbf{Psalm 68:26} - Bless ye God in the congregations, even the Lord, from the fountain of Israel.}\footnote{\textbf{Psalm 74:4} - Thine enemies roar in the midst of thy congregations; they set up their ensigns for signs.} The word ``congregation,'' on the other hand, is used 364 times, only once in the New Testament. The first occurrence is in Exodus 12:3 and the last in Acts 13:43.\footnote{\textbf{Exodus 12:3} - Speak ye unto all the congregation of Israel, saying, In the tenth day of this month they shall take to them every man a lamb, according to the house of their fathers, a lamb for an house:}\footnote{\textbf{Acts 13:43} - Now when the congregation was broken up, many of the Jews and religious proselytes followed Paul and Barnabas: who, speaking to them, persuaded them to continue in the grace of God.}