\section{Psalm 43 Comments}

\subsection{Numeric Nuggets}
\textbf{8: } The name ``God'' is used eight times in the psalm. With eight being the number for newness, the psalmist looks to God to be re-energized in his walk.

\subsection{Psalm 43:1}
And just what is an ``ungodly nation''? Consider Ruckman's comments, as he points the United States of America, where:\begin{compactenum}
\item One divorce out of two marriages.
\item Twenty thousand deaths a year through drunken driving.
\item Ten hundred thousand abortions a year.
\item Fourteen million chronic alcoholics.
\item The highest murder and rape rate in the world.
\item Six million Sodomites.
\item Nude and half nude models on Magazine covers where ten year olds can see them.
\item The most lucrative pornography traffic in the world.
\item Fifteen million people on crack, cocaine, heroine, or marijuana.
\item Five thousand ministers who don't believe in Genesis, chapters 1-–3, a literal Heaven or Hell, or the Second Coming. 
\end{compactenum} 
In contrast, a ``righteous nation'' is defined (Isaiah 26:20) as one that keeps God's truth. Consider, further, the kinds of nations described in scripture: \begin{inparaenum} [(1.)]\item a righteous nation (Genesis 20:4) (this is what Abimelech calls his own people) \item an holy nation (Exodus 19:6, 1 Peter 2:9) \item a foolish nation (Deuteronomy 32:21, foolish nation) \item a nation void of counsel (Deuteronomy 32:28) \item ungodly nation (Psalm 43:1) \item a sinful nation (Isaiah 1:4) \item an hypocritical nation (Isaiah 10:6) \item a nation meted out and trodden under foot (Isaiah 18:2, 7) \item a righteous nation (Isaiah 26:2) \item a mighty nation (Jeremiah 5:15) \item an ancient nation (Jeremiah 5:15) \item a great nation (Jeremiah 6:22, 50:41) \item a rebellious nation (Ezekiel 2:3) \item a bitter and hasty nation (Habakkuk 1:6) \item a perverse nation (Philippians 2:15).\end{inparaenum} \cite{Ruckman1992Psalms} 

