\section{Psalm 37 Outlines}

\subsection{My Outlines}

\subsubsection{Looking Back}
\index[speaker]{Keith Anthony!Psalm 037:25 (Looking Back)}
\index[series]{Psalms (Keith Anthony)!Psalm 037:25 (Looking Back)}
\index[date]{2016/10/09!Psalm 037:25 (Looking Back) (Keith Anthony)}
\textbf{Introduction: }This past week, I've watched someone pass a significant age milestone, but it is one I passed quite a while ago.  I have always liked Psalm 37, but especially verse 25\index[scripture]{Psalms!Psa 037:25}. The verse talks about some inevitable things, like getting old.  And, it talks about some certain things for a Christian, such as God never forsaking his people and always providing for them. I have seen this in my 38 years of being a Christian, and I've seen other things. So, this is a short commentary on my first 38 years of Christianity. \footnote{09 October 2016, Keith Anthony}
\begin{compactenum}[I.][19]
    \item A \textbf{Slow Burn.} \index[scripture]{Hebrews!Heb 12:01}(Hebrews 12:1) I see this in at least two ways.  First there is the long \textbf{race}, a marathon, for believers. Christianity is not a print: it is a distance event. Christianity is a tedious and day-by-day journey. The second aspect is that of \textbf{refining}. I am thankful that the refining in my life, a necessary thing, has been a slow burn. Look at Psalm 12:6-7. Like the completion of a perfect Bible, refining uses fire and heat to burn out impurities and imperfections. I don't like pain. I don't like trouble. I don't like trials. I really don't even like heat and fire.  I don't like getting burned! Maybe a slow and steady refinement is a good thing. 
    \item \textbf{Speed Bumps.} Another thing I've encountered along my Christian experience is speed bumps.  These have been times when big events or situations have knocked my off the slow and steady, maybe even predictable, path. It is especially important to note that many, if not all, of these have been of my OWN doing.  It may be a scandalous thing, but God has gotten me through each of these. %\index[scripture]{Hebrews!Hebrews 12:01}(Hebrews 12:1) 
    \item All \textbf{Sorts of Brethren.} Another part of Christianity has been the fact that God has brought all sorts of brethren into my life. Some have passed.  Some are close at hand. All, though, have made part of my life for a specific reason. Some I have helped. Many more have helped me. Some ... I don't know yet! For some, the next time I see them will be in heaven where for eternity we can talk of God's goodness. %\index[scripture]{Hebrews!Hebrews 12:01}(Hebrews 12:1
    \item A \textbf{Special Book.} One thing that has motivated my Christianity has been the Bible.  I for one cannot understand any Christian who does not have a burning and consuming passion to understand every word in it.  What does one actually do with a perfect and living book? Open it up once or twice a week? Ignore it when it is inconvenient? Its a whole new ball game when you recognize the Bible for what it is .... %\index[scripture]{Hebrews!Hebrews 12:01}(Hebrews 12:1) 
    \item A \textbf{Solid Beliefs.} God gives us solid, consistent, and reliable body of beliefs and then He proves them over and over again.  Beliefs such as saved by grace alone, belief that all things work together for good to those who love God, belief that God's word will not return void!%\index[scripture]{Hebrews!Hebrews 12:01}(Hebrews 12:1) 
    \item \textbf{Special Blessings.} God graces us with special blessings. How about time I got to lead my son to the Lord? What about my grandchildren? What about God providing direction in life and leading to a church where scripture is magnified?  %\index[scripture]{Hebrews!Hebrews 12:01}(Hebrews 12:1)
    %\item A \textbf{Splendid Bride.} 
    \item A \textbf{School Building.} So salvation is just the beginning.  The rest of Christian life is getting to know God, getting to know truth, getting to learn how to be blessing to God and his people. %\index[scripture]{Hebrews!Hebrews 12:01}(Hebrews 12:1)
    \item (Looking Ahead) A \textbf{Spectacular Baccalaureate (Graduation).} Finally, I have something quite unique to look forward to and that is what comes after this life. Turn to 1 Corinthians 2:9. Now think of the best thing that has happened to you in this life.  It will be incomparable to what awaits the believer. %\index[scripture]{Hebrews!Hebrews 12:01}(Hebrews 12:1) 
\end{compactenum}


\subsubsection{When the Wicked Triumph}

\index[speaker]{Keith Anthony!Psalm 037 (When the Wicked Triumph)}
\index[series]{Psalms (Keith Anthony)!Psalm 037 (When the Wicked Triumph)}
\index[date]{2016/07/13!Psalm 037 (When the Wicked Triumph) (Keith Anthony)}

\begin{compactenum}[I.][19]
    \item An \textbf{Apparent Problem} \index[scripture]{Psalms!Psa 037:01}(Psalm 37:1) 
    \item \textbf{Abandoned Paths} \index[scripture]{Psalms!Psa 037:01-11}(Psalm 37:1--11)
    \item \textbf{Awesome Prophecies} \index[scripture]{Psalms!Psa 037:01-40}(Psalm 37:1--40)
    \item \textbf{Attractive Pursuits} \index[scripture]{Psalms!Psa 037:11-22}(Psalm 37:11--22)
    \item \textbf{Abiding Principles} \index[scripture]{Psalms!Psa 037:32-40}(Psalm 37:32--40)
    \item \textbf{Almighty Preservation} \index[scripture]{Psalms!Psa 037:28}(Psalm 37:28)
    \item \textbf{Absolute Promises} \index[scripture]{Psalms!Psa 037:01-11}(Psalm 37:1--11)
\end{compactenum}

%\subsubsection{Prayer for Israel's Time of Trouble}
%Key words in Psalm 37 include ``fret'' (found 3 times) and ``inherit'' (found 5 times in Psalm 37:9, Psalm 37:11, Psalm 37:22, Psalm 37:29 and Psalm 37:34). :\footnote{05 December 2014, \textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{PsalmsTOC}{Return to end of Table of Contents.}}}
%\begin{compactenum}[I.]
%    \item The Wicked Have No \textbf{No Fear of God} (\index[scripture]{Psalm!Psalm  36: 1}Psalm 36: 1)
%    \item The Wicked Practice \textbf{Self Flattery} (\index[scripture]{Psalm!Psalm  36: 2}Psalm 36: 2)
%    \item The Wicked Miss the \textbf{Faithfulness of God} (\index[scripture]{Psalm!Psalm  36: 5}Psalm 36: 5)
%    \item The Faithful Partake of the \textbf{Fatness of God's House} (\index[scripture]{Psalm!Psalm  36: 8}Psalm 36: 8)
%    \item The Faithful Partake of the \textbf{Fountain of Life} (\index[scripture]{Psalm!Psalm  36: 9}Psalm 36: 9)
%    \item The Faithful are Delivered from the \textbf{Foot of Pride} and the Hand of the Wicked (\index[scripture]{Psalm!Psalm  36: 9}Psalm 36: 9)
%    \item The Wicked will \textbf{Fall and Not Rise} (\index[scripture]{Psalm!Psalm  36:12}Psalm 36:12)
%\end{compactenum}

\subsection{Outlines from Others}




